---
title: 'Class Activity: Linear-Mixed Effects Models for Hierarchical Data'
subtitle: 'STAT 340: Applied Regression'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# Exam scores from Inner London

```{r}
library(lmer)
library(nlme)
library(mlmRev)
data(Exam)
```

- `school`: School ID (a factor)
- `normexam`: Normalized exam score
- `schgend`: School gender (a factor); levels are `mixed`, `boys`, `girls`
- `schavg`: School average of intake score
- `vr`: Student level Verbal Reasoning (VR) score band at intake (a factor). Levels are `bottom 25%`, `mid 50%`, `top 25%`
- `standLRT`: Standardized LR test score
- `sex`: Sex of the student - levels are `F` and `M`
- `type`: School type - levels are `Mxd` and `Sngl`
- `student`: Student id (within school, a factor)

### (1) Identify which variables are on the School level, and which are on the student level. Would you consider any modifications to these variables (like centering)?



### (2) Fit the null model for `normexam`, with a fixed intercept and a random intercept.

```{r}

```


### (3) Fit a linear mixed-effects model for `normexam`, with a random intercept and `schavg` as a fixed effect.

```{r}

```

### (4) Fit a linear mixed-effects model for `normexam`, with fixed effects for `standLRT` and `schavg`, and a random intercept and random effect for `standLRT`. What assumption does this make about `standLRT`? Would you recommend any modifications (think Question 1)?

```{r}

```

